Manuscript1_figures

### 2025-05-06 Manuscript1_figures.Rmd
Changing "pre" vs "post" TO categorization to better reflect overlapping 2018 FCR and BVR sampling periods. Updating Figure S3 and flux summary table.

avgFluxes2018_2023 <- fluxes2018_2023 %>% 
  group_by(Reservoir, Date, Depth_m, Layer, Year) %>% 
  summarise(Duration_days = mean(Duration_days),
            AvgTFeFlux_gm2d = mean(TFeFlux_gm2d, na.rm = TRUE),
            AvgTMnFlux_gm2d = mean(TMnFlux_gm2d, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(TO = NA,
         #2018, only include data points from FCR that match data points from BVR
         TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
                      & Date < as.Date('2018-09-03'), 'Pre_', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
                      & Date < as.Date('2018-07-23'), 'Pre_', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
                      & between(Date, as.Date('2018-09-03'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
                      & between(Date, as.Date('2018-07-23'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' 
                      & Date <= as.Date('2018-09-07'), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'FCR' 
                      & Date >= as.Date('2018-10-21'), 'Post', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' 
                      & Date >= as.Date('2018-10-21'), 'Post', TO),
         #2019
         TO = if_else(Year == 2019 & Reservoir == 'FCR' & Date < as.Date('2019-10-24'), 'Pre', TO),
         TO = if_else(Year == 2019 & Reservoir == 'BVR' & Date < as.Date('2019-10-30'), 'Pre', TO),
         TO = if_else(Year == 2019 & Reservoir == 'FCR' & Date >= as.Date('2019-10-24'), 'Post', TO),
         TO = if_else(Year == 2019 & Reservoir == 'BVR' & Date >= as.Date('2019-10-30'), 'Post', TO),
         #2020
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         #2021
         TO = ifelse(Year == 2021 & Reservoir == 'FCR' & Date < as.Date('2021-11-03'), 'Pre', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'BVR' & Date < as.Date('2021-11-05'), 'Pre', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'FCR' & Date >= as.Date('2021-11-03'), 'Post', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'BVR' & Date >= as.Date('2021-11-05'), 'Post', TO),
         #2022
         TO = ifelse(Year == 2022 & Reservoir == 'FCR' & Date < as.Date('2022-10-20'), 'Pre', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'BVR' & Date < as.Date('2022-10-19'), 'Pre', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'FCR' & Date >= as.Date('2022-10-20'), 'Post', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'BVR' & Date >= as.Date('2022-10-19'), 'Post', TO),
         #2023
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date >= as.Date('2023-11-02'), 'Post', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date >= as.Date('2023-11-02'), 'Post', TO)) %>% 
  arrange(Date)

@@

DO4 <- Handhelds %>% 
  mutate(Date = date(DateTime),
         Year = year(DateTime)) %>% #HOx activated on 2018-04-23 @ noon
  filter(Year == 2018| Year == 2019 | Year == 2020,
         Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2018-05-04'), as.Date('2018-12-05'))|
           Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2019-05-18'), as.Date('2020-03-14'))|
           Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2020-05-16'), as.Date('2020-06-17'))|
           Reservoir == 'FCR' & Depth_m == 9 & Date < as.Date('2018-08-19')) %>% 
  select(Reservoir, Site, Date, Year, Depth_m, DO_mgL) %>% 
  mutate(Depth_m = factor(Depth_m),
         Method = 'edi.198.13') %>% 
  drop_na()

DO <- DO1 %>% 
  full_join(DO2) %>% 
  full_join(DO3) %>%
  full_join(DO4) %>% 
  filter(Date <= as.Date('2023-12-31')) %>%
  mutate(Method = factor(Method, levels = c('edi.271.9', 'edi.725.5', 'edi.198.13'))) %>%
  ungroup() %>% 
  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-11-17'),
  #        Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
  #        Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'FCR', Site = 50, Date = as.Date('2018-08-19'),
          Year = 2018, Depth_m = as.factor(9), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-12-05'),
          Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-05-17'),
          Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-10-18'),
  #        Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
  #        Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-01-01'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.725.5')) %>% 
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-03-15'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>% 
    add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-05-15'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-06-05'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13')) %>%
arrange(Date)

DO_plot1 <- DO %>% 
  ggplot() +
  scale_x_date(name = '', date_breaks = '1 year', date_labels = '%Y') +
  theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir, linetype = Method)) +
  scale_linetype_manual(values = c('solid', 'solid', 'dotted')) + 
  guides(linetype = guide_legend(title = 'Data Package')) +
  ylab('Dissolved Oxygen (mg/L)')
```

@@

## Tables
```{r Tables script, eval=TRUE, include=FALSE}
AvgFluxSummary2018_2023 <- avgFluxes2018_2023 %>% 
  filter(TO == 'Pre') %>% 
  group_by(Reservoir, Layer) %>% 
  summarise(MeanFeFlux = round(mean(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MeanMnFlux = round(mean(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MedianFeFlux = round(median(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MedianMnFlux = round(median(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MinFeFlux = round(min(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MaxFeFlux = round(max(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MinMnFlux = round(min(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MaxMnFlux = round(max(AvgTMnFlux_gm2d, na.rm = T), digits = 3)) %>% 
  ungroup()

@@

#Figure 6
ggsave(DO_MaxMetal_plotFinal, file = 'DOps_MaxMetal.png', path = myFilePath,
       height = 5, width = 8, units = 'in')
#Figure 7
ggsave(plot = ComboFluxPlot, filename = 'CumulHypFlux_tTest_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure 8
ggsave(plot = HypCumulFluxPlot, filename = 'CumulHypFlux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure 9
ggsave(comboPlot1, file = 'STFeMn_2020_2023.png', path = myFilePath, height = 6, width = 8, units = 'in')
#Figure S1
ggsave(plot = FluxPlot, filename = 'Flux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure S3
ggsave(DO_plot1, file = 'HypolimnionDO_2018_2023.png', path = myFilePath, height = 4, 
       width = 6, units = 'in')
#Figure S4
ggsave(DO_CumulMetal_plotFinal, file = 'DOps_MaxMetal.png', path = myFilePath,
       height = 5, width = 8, units = 'in')
```

>>>>

avgFluxes2018_2023 <- fluxes2018_2023 %>% 
  group_by(Reservoir, Date, Depth_m, Layer, Year) %>% 
  summarise(Duration_days = mean(Duration_days),
            AvgTFeFlux_gm2d = mean(TFeFlux_gm2d, na.rm = TRUE),
            AvgTMnFlux_gm2d = mean(TMnFlux_gm2d, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(TO = NA,
         #2018, only include data points from FCR that match data points from BVR
         TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
                      & Date < as.Date('2018-09-02'), 'Pre_', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
                      & Date < as.Date('2018-07-22'), 'Pre_', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
                      & between(Date, as.Date('2018-09-02'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
                      & between(Date, as.Date('2018-07-22'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' & Layer == 'Epilimnion' 
                      & between(Date, as.Date('2018-09-06'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' & Layer == 'Hypolimnion' 
                      & between(Date, as.Date('2018-08-01'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'FCR' 
                      & Date >= as.Date('2018-10-21'), 'Post', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' 
                      & Date >= as.Date('2018-10-21'), 'Post', TO),
         #2019
         TO = if_else(Year == 2019 & Reservoir == 'FCR' & Date < as.Date('2019-10-24'), 'Pre', TO),
         TO = if_else(Year == 2019 & Reservoir == 'BVR' & Date < as.Date('2019-10-30'), 'Pre', TO),
         TO = if_else(Year == 2019 & Reservoir == 'FCR' & Date >= as.Date('2019-10-24'), 'Post', TO),
         TO = if_else(Year == 2019 & Reservoir == 'BVR' & Date >= as.Date('2019-10-30'), 'Post', TO),
         #2020
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         #2021
         TO = ifelse(Year == 2021 & Reservoir == 'FCR' & Date < as.Date('2021-11-03'), 'Pre', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'BVR' & Date < as.Date('2021-11-05'), 'Pre', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'FCR' & Date >= as.Date('2021-11-03'), 'Post', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'BVR' & Date >= as.Date('2021-11-05'), 'Post', TO),
         #2022
         TO = ifelse(Year == 2022 & Reservoir == 'FCR' & Date < as.Date('2022-10-20'), 'Pre', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'BVR' & Date < as.Date('2022-10-19'), 'Pre', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'FCR' & Date >= as.Date('2022-10-20'), 'Post', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'BVR' & Date >= as.Date('2022-10-19'), 'Post', TO),
         #2023
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date >= as.Date('2023-11-02'), 'Post', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date >= as.Date('2023-11-02'), 'Post', TO)) %>% 
  arrange(Date)

@@

DO4 <- Handhelds %>% 
  mutate(Date = date(DateTime),
         Year = year(DateTime)) %>%
  filter(Year == 2018| Year == 2019 | Year == 2020,
         Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2018-05-04'), as.Date('2018-12-05'))|
           Reservoir == 'BVR' & Depth_m == 10 & 
           between(Date, as.Date('2019-05-18'), as.Date('2020-03-14'))|
           Reservoir == 'FCR' & Depth_m == 9 & Date < as.Date('2018-08-19')) %>% 
  select(Reservoir, Site, Date, Year, Depth_m, DO_mgL) %>% 
  mutate(Depth_m = factor(Depth_m),
         Method = 'edi.198.13') %>% 
  drop_na()

DO <- DO1 %>% 
  full_join(DO2) %>% 
  full_join(DO3) %>%
  filter(Date <= as.Date('2023-12-31')) %>% 
  ungroup() %>% #adding NAs to create appropriate line breaks
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-01-01'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.725.5')) %>%
  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-05-15'),
          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
          Method = as.factor('edi.198.13'))

DO_plot1 <- DO %>% 
  ggplot() +
  scale_x_date(name = '', date_breaks = '1 year', date_labels = '%Y') +
  theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir)) +
  geom_point(aes(x = Date, y = DO_mgL, color = Reservoir), data = DO4, size = 0.5) +
  ylab('Dissolved Oxygen (mg/L)')
```

@@

## Tables
```{r Tables script, eval=TRUE, include=FALSE}
AvgFluxSummary2018_2023 <- avgFluxes2018_2023 %>% 
  filter(TO == 'Pre') %>% 
  group_by(Reservoir, Layer, Year) %>% 
  summarise(MeanFeFlux = round(mean(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MeanMnFlux = round(mean(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MedianFeFlux = round(median(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MedianMnFlux = round(median(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MinFeFlux = round(min(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MaxFeFlux = round(max(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MinMnFlux = round(min(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MaxMnFlux = round(max(AvgTMnFlux_gm2d, na.rm = T), digits = 3)) %>% 
  ungroup()

@@

#Figure 6
ggsave(DO_MaxMetal_plotFinal, file = 'DOps_MaxMetal.png', path = myFilePath,
       height = 5, width = 8, units = 'in')
#Figure 7
ggsave(plot = ComboFluxPlot, filename = 'CumulHypFlux_tTest_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure 8
ggsave(plot = HypCumulFluxPlot, filename = 'CumulHypFlux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure 9
ggsave(comboPlot1, file = 'STFeMn_2020_2023.png', path = myFilePath, height = 6, width = 8, units = 'in')
#Figure S1
ggsave(plot = FluxPlot, filename = 'Flux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure S3
ggsave(DO_plot1, file = 'HypolimnionDO_2018_2023.png', path = myFilePath, height = 4, 
       width = 8, units = 'in')
#Figure S4
ggsave(DO_CumulMetal_plotFinal, file = 'DOps_MaxMetal.png', path = myFilePath,
       height = 5, width = 8, units = 'in')
```
